Parallel global optimization algorithm with uniform convergence for solving a set of constrained global optimization problems\thanks{This study was supported by the Russian Science Foundation, project No.\,16-11-10150.}

### 2020-09-16 2020/OPTIMA/Answers.tex
OPTIMA: update answers

@@

\textbf{Answer}.
Результаты сравнения core Global Search Algorithm с рядом nature-inspired methods при решении нескольких сотен тестовых задач приведены в [1]. Результаты показывают, что GSA обеспечивает лучшее качество решения задач (решается большее число задач за меньшее число поисковых испытаний). В текст статьи добавлен соответствующий комментарий (see page ...).

Еще раз отметим, что в работе рассматриваются задачи с функциями вида ``черный ящик'' (i.e., an analytical representation of the functions is not available). Поэтому сравнение с методами, использующими аналитическое представление функций задачи (например, основанными на идеях DC-оптимизации, see [2] and references given therein) не будет являться корректным. В текст статьи добавлен соответствующий комментарий (see page ...).

@@

@@

>>>>

\textbf{Answer}.
Clarification of the objective of this work was added to the end of the Section 2.

@@

\textbf{Answer}.
Результаты сравнения core Global Search Algorithm с рядом nature-inspired methods при решении нескольких сотен тестовых задач приведены в [1]. Результаты показывают, что GSA обеспечивает лучшее качество решения задач (решается большее число задач за меньшее число поисковых испытаний). В текст статьи добавлен соответствующий комментарий (see page 11).

Еще раз отметим, что в работе рассматриваются задачи с функциями вида ``черный ящик'' (i.e., an analytical representation of the functions is not available). Поэтому сравнение с методами, использующими аналитическое представление функций задачи (например, основанными на идеях DC-оптимизации, see [2] and references given therein) не будет являться корректным. В текст статьи добавлен соответствующий комментарий (see page 2).

@@

\textbf{Answer}.
The presented method converges to all the global optimal solutions at once, but numerically it's hard
to obtain them all with a guarentee. That happens because of luck of an appropriate stopping criterion.

@@

A serie of global optimization problems can arise from an mixed-integer problem or
after scalarization [1] of an multi-objective problem [2]. In both cases it's needed to
solve all the problems from the serie approximetely with the same quality, because all of
them are equally important. To speedup this process under constrained computational resources,
we can apply parellelism in couple with a resource balancing approach to guarantee equal
quality of solutions in all the problems by the end of the optimization process.

1. Barkalov, K. and I. Lebedev. “Parallel Global Optimization for Non-convex Mixed-Integer Problems.” RuSCDays (2019).

2. Jahn J. Scalarization in Multi Objective Optimization. In: Serafini P. (eds) Mathematics of Multi Objective Optimization. International Centre for Mechanical Sciences (Courses and Lectures), vol 289. Springer, Vienna (1985).

### 2020-09-16 2020/OPTIMA/optima_paper.tex
OPTIMA: update answers

\section{Introduction}
\label{sec-intro}
Global optimization problems with non-convex constraints are considered to be one
of the most difficult optimization problems.
Finding of the global minimum of a function of several variables appears to be more
difficult often than a local optimization in a thousand-dimensional space.
For the latter, application of the simplest gradient descent method may appear to be enough,
whereas to \textit{guarantee} the finding of the global optimum the optimization
methods have to accumulate the information on the behaviour of the objective function in the
whole search domain \cite{Jones2009,Paulavicius2011,Evtushenko2013,Strongin2000}.
The solving of a series of such problems at limited computational resources is even more
difficult problem: besides the search of the global extremum, it is necessary to distribute the
computational resources in such a way that the location of the global extremum would be
estimated with approximately equal quality in all problems being solved at once.
Usually, a series of \(q\) problems is solved either sequentially or in parallel by portions of \(p\ll
q\) problems where \(p\) is a number of parallel computational devices.
Such an approach leads to a situation when at every time moment until the stop of computations
some problems remain, in which the estimate of the global optimum is not obtained yet whereas
in the problems from the beginning of the list the optimum may be estimated even with excess
precision.

@@

In order to demonstrate the uniform convergence of MIAGS, all test problems have been solved by IAGS as well.
Fig. \ref{fig:devs_mixed} presents the plots of mean and maximum distances from the actual
optima to the current estimates of these ones when solving a series of problems generated by
two different generators separately (solid line) and together (dashed line).
In spite of an essential differences in the structure of problems, the MIAGS decreased
the maximum deviations of the estimates from the optima as well as the mean ones much faster.
It evidences the uniform convergence over the whole set of problems being solved all together.
At that, in the case of the sequential solving of the problems, the magnitude \(D_{max}\) takes
its maximum value until the last problem is solved.

>>>>

\section{Introduction}
\label{sec-intro}
Global optimization problems with non-convex constraints are considered to be one
of the most difficult optimization problems.
Finding of the global minimum of a function of several variables appears to be more
difficult often than a local optimization in a thousand-dimensional space.
For the latter, application of the simplest gradient descent method may appear to be enough,
whereas to \textit{guarantee} the finding of the global optimum the optimization
methods have to accumulate the information on the behavior of the objective function in the
whole search domain \cite{Jones2009,Paulavicius2011,Evtushenko2013,Strongin2000}.
In some cases, like for DC or QP problems, one can propose more effective methods and even
analytical optimality conditions \cite{PhamDinh2014, qpBook}, but when we have to deal with black box functions
(i.e., an analytical representation of the functions is not available) these methods are barely applicable.

The solving of a series of such problems at limited computational resources is even more
difficult problem: besides the search of the global extremum, it is necessary to distribute the
computational resources in such a way that the location of the global extremum would be
estimated with approximately equal quality in all problems being solved at once.
Usually, a series of \(q\) problems is solved either sequentially or in parallel by portions of \(p\ll
q\) problems where \(p\) is a number of parallel computational devices.
Such an approach leads to a situation when at every time moment until the stop of computations
some problems remain, in which the estimate of the global optimum is not obtained yet whereas
in the problems from the beginning of the list the optimum may be estimated even with excess
precision.

@@

In order to demonstrate the uniform convergence of MIAGS, all test problems have been solved by IAGS as well.
IAGS is comparable with other stochastic and deterministic derivative-free global optimization algorithms \cite{Sovrasov2019}. Thus it
provides a strong baseline in solving a single global optimization problem.
Fig. \ref{fig:devs_mixed} presents the plots of mean and maximum distances from the actual
optima to the current estimates of these ones when solving a series of problems generated by
two different generators separately (solid line) and together (dashed line).
In spite of an essential differences in the structure of problems, the MIAGS decreased
the maximum deviations of the estimates from the optima as well as the mean ones much faster.
It evidences the uniform convergence over the whole set of problems being solved all together.
At that, in the case of the sequential solving of the problems, the magnitude \(D_{max}\) takes
its maximum value until the last problem is solved.
